### 2022-05-20 project_Luis/paper.tex
fixing compile
Fix compile
updates

\documentclass[final,12pt]{article}
\usepackage{graphicx}
\usepackage[letterpaper,margin=1.0in]{geometry}
\usepackage{amssymb}
\usepackage{changepage}
\usepackage{float}
\usepackage{hyperref}
\usepackage{url}
\usepackage{afterpage}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\usepackage[utf8]{inputenc} 
\usepackage{lastpage}

\def\Student{Luis Enrique CUEVAS PICOS }
\def\Title{MASTERS THESIS PROJECT}
\def\TitleESP{(ANTEPROYECTO)}
\def\Prog{Maestria en Ciencias (F\'{i}sica) }
%\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Dept{DIFUS}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Development and calibration of the luminosity measurement system CMS Silicon Pixel Detector}
\def\ProjectTitleESP{Desarrollo y calibraci\'{o}n del sistema de medici\'{o}n de luminosidad CMS Silicon Pixel Detector}
\def\ResearchLine{Fisica Matematica}

@@

%%%%%%%comands
\newcommand{\SubItem}[1]{ {\setlength\itemindent{15pt} \item[-] #1} }
\newcommand{\lumi}[1]{{#1~fb$^{-1}$}}
\newcommand{\instlumi}[1]{#1$\times 10^{34}$ cm$^{-2}$s$^{-1}$}

@@

  \vspace{1cm}
  {
    TITLE:\par
    {\bf \large \ProjectTitle  \par}

    \vspace{0.4cm}
    TITULO:\par
    {\bf \large \ProjectTitleESP \par}
  }

@@

  This  project consists on  perform an analysis and calibration of the LHC luminosity data recorded
by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method, to develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
Luminosity gives a measure of how many collisions are happening in a particle accelerator  and a precise determination of this will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
The (PCC) method is an offline technique for the calculation of instantaneous luminosity  by counting the number of pixel clusters in the detector.
The high densities of pixels of the Inner Tracker gives a low hit occupancy in the sensors during the proton-proton collisions, this leads to a very linear response and small  uncertainties for the luminosity measurement.   
  \hspace{2pt}
\vfill

@@

Luminosity, $L$, is a key parameter at particle colliders along with the energy available in the collision.
$L$ is one of the  main figures of merit that quantify the potential for observing new particles and measuring their properties.
The instantaneous luminosity $L(t)$ is the process-independent ratio between the rate $R(t)$ of events produced per unit time and the cross section for a given process $\sigma$: $L(t) = R(t)/\sigma$.
During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$.
For comparison, the total Higgs production cross section is 48600 fb.}.
In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt-corr}.
For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined and is the main objective of this thesis project \cite{CMS:2018elu-corr}.

@@

We propose to perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method. To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC.

@@

To perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method. To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
This will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.

@@

 \cite{Dainese:3}.

\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\end{itemize}

@@

@@

\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

>>>>

\documentclass[final,12pt]{article}
\usepackage{graphicx}
\usepackage[letterpaper,margin=1.0in]{geometry}
\usepackage{amssymb}
\usepackage{changepage}
\usepackage{float}
\usepackage{hyperref}
\usepackage{url}
\usepackage{afterpage}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\usepackage[latin1]{inputenc} 
\usepackage{lastpage}

\def\Student{Luis Enrique CUEVAS PICOS }
\def\Title{MASTERS THESIS PROJECT}
\def\TitleESP{(ANTEPROYECTO)}
\def\Prog{Maestria en Ciencias (F\'{i}sica) }
%\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Dept{DIFUS}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Studies of the CMS Pixel Cluster Counting luminometer using Run 3 data}
\def\ProjectTitleESP{Estudios del luminometro Pixel Cluster Counting del CMS usando datos de la corrida 3}
\def\ResearchLine{Fisica Matematica}

@@

%%comands
\newcommand{\SubItem}[1]{ {\setlength\itemindent{15pt} \item[-] #1} }
\newcommand{\lumi}[1]{{#1~fb$^{-1}$}}
\newcommand{\instlumi}[1]{#1$\times 10^{34}$ cm$^{-2}$s$^{-1}$}

@@

  \vspace{1cm}
  {
    TITLE:\par
    {\bf \large \ProjectTitle  \par}
    \vspace{\baselineskip}   
    \vspace{0.4cm}
    TITULO:\par
    {\bf \large \ProjectTitleESP \par}
  }

@@

  This  project consists on  perform an analysis and calibration of the LHC luminosity data recorded
  by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
%to develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
Luminosity gives a measure of how many collisions are happening in a particle accelerator  and a precise determination of this will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
The PCC method is an offline technique for the calculation of instantaneous luminosity  by counting the number of pixel clusters in the detector.
The high densities of pixels of the Inner Tracker of the CMS detector gives a low hit occupancy in the sensors during the proton-proton collisions, this leads to a very linear response and small  uncertainties for the luminosity measurement.   
  \hspace{2pt}
\vfill

@@

Luminosity, $L$, is a key parameter at particle colliders along with the energy available in the collision.
$L$ is one of the  main figures of merit that quantify the potential for observing new particles and measuring their properties.
The instantaneous luminosity $L(t)$ is the process-independent ratio between the rate $R(t)$ of events produced per unit time and the cross section for a given process $\sigma$: $L(t) = R(t)/\sigma$.
During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$.
For comparison, the total Higgs production cross section is 48600 fb.}.
In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt-corr}.
For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}.
%but its precise value and uncertainty remain to be determined and is the main objective of this thesis project \cite{CMS:2018elu-corr}.
After many upgrades to the different parts of the experiment, Run 3 is restarting this year 2022.
The main objective of this thesis project is to analize the first data recorded this year and provide a preliminary result of the luminosity recorded by the CMS experiment.

@@

We propose to perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
In particular, we plan to perform studies of detector components and the calibration data recording using the van Der Meer (vdM) scans that allow to obtain the calibration of this luminometer with high precision.
%To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC.

@@

To perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
%To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
This will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.

@@

For this preliminary measurement of the luminosity data collected in 2022, we expect that the methods used in this analisis will lead to a measurement uncertainty better than 2\%. 
% \cite{Dainese:3}.

@@

\begin{itemize}
\item

@@

\begin{itemize}
\item
